Supplementary Materials

### 2020-05-15 analysis/analysis.Rmd
p2, p3, p4, p6 comparison

>>>>

## Replicatation of Kohler et al (2016)

We can lok at the groups that only contain orientation, and see if we obtain the parametric response as documented in Kohler et al. (2016). We one might predict based on those results, we get a corresponding pattern of display duration thresholds, with the time taken to detect the symmetry dreasing as we increase the amount of rotational symmetry.

Curiosuly, we do not have a large difference betwee P4 and P6 in the eeg data.

```{r, fig.cap = "The effect of increasing the amount of rotational symmetry.", fig.height=3}
my_samples$eeg %>% select(P2, P3, P4, P6) %>%
  pivot_longer(names_to = "wallpaper group", cols = c(P2, P3, P4, P6)) %>% 
  mutate(exp = "eeg") %>%
  bind_rows(
    my_samples$threshold %>% select(P2, P3, P4, P6) %>% 
      pivot_longer(names_to = "wallpaper group", cols = c(P2, P3, P4, P6)) %>%
      mutate(exp = "display thresholds")) %>% 
  ggplot() + aes(x = value, fill = `wallpaper group`) + 
    geom_density(alpha = 0.35) + 
    facet_wrap(~ exp, scale = "free_y") + 
  theme_minimal() + 
  scale_fill_viridis_d()
```
